### 2016-05-28 sec1_introduction.tex
Added intro part

A crucial task of data analysis on top of trajectories is 
to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined according to spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-moving patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering method and length of temporal duration. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
spatial clustering in determining groups. 
In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

%Specifically, a \emph{flock}~\cite{gudmundsson2006flock} requires the group to be within a disk region of
%the user specified size.  A \emph{convoy}~\cite{jeung2008convoy} requires a group to be densely connected. Both \emph{flock}
%and \emph{convoy} require a group to appear for at least $k$ consecutive times.  
%\emph{Group}~\cite{wang2006grouppattern} and 
%\emph{Swarm}~\cite{li2010swarm} patterns relax the consecutiveness constraint, where non-consecutive timestamps are allowed in a pattern duration. \emph{Group} pattern require objects in a group to be within a disk region, while \emph{swarm}require the objects in a group to be densely connected.
%Recently,
%\emph{platoon}~\cite{li2015platoon} pattern is proposed to impose a fine-grained control on the consecutiveness of the duration. In \emph{platoon}, the duration of a group needs to have the local-consecutive portion of size no less than the user-specified $L$.

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles.}
\label{fig:related_work}
\end{figure}

%%We first provide a synthetic example to better illustrate these patterns in Figure~\ref{fig:related_work}, and the formal definitions are described in Section~\ref{sec:definition}.
%UPDATE THE FIGURE TO CONTAIN SIX SNAPSHOTS. USE A NEW REPRESENTATION OF THE PATTERN. I DON'T LIKE $\{o_1,o_2\}\{1,2,3\}$. USE ONE PAIR OF $\{\}$ ONLY.

We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
The temporal dimension is discretized into six snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

% we achieve two \emph{platoon} patterns.
% 
%By setting $M=2$, the spatial clusters with at least $2$ objects are displayed with the same shape. Since \emph{Convoy} pattern requires the set of objects to be clustered for $k$ \emph{consecutive} snapshots, there results in only one such pattern ($\{o_3,o_4\}\{t_1,t_2,t_3\}$) when $k$ is set to $3$. \emph{Swarm} pattern relaxes the consecutiveness of duration, thus there are three patterns discovered. \emph{Platoon} pattern requires that each local consecutive duration needs to have at least certain length, which is indicated by an additional parameter $l$. When $l$ equals 2, there are two patterns discovered. Note that $\{o_6,o_7\}\{t_1,t_4,t_5\}$ is not included in the platoon pattern since $t_1$ is the local consecutive snapshot with duration 1, which is less than $l$. CAN WE SUPPORT THE GROUP AND FLOCK PATTERN? IF YES, WHY NOT PUT THEM IN THE FIGURE?
%
%FOR THE FIGURE: 1) ENLARGE THE FONT SIZE IN THE FIGURE 2) WHY THERE IS NO $o_5$. 3) WHY OBJECTS IN DIFFERENT COLORS AND SHAPES ARE NOT CLEAR. YOU CAN REMOVE COLOR. 4) PUT THE OBJECTS BELONGING TO THE SAME CLUSTER IN THE SAME LINE.

%We notice that, \emph{platoon} pattern is more general than \emph{convoy} and \emph{swarm}. This is because by setting appropriate $l$, \emph{platoon} can be reduced to \emph{convoy} and \emph{swarm} respectively~\cite{li2015platoon}. However, we observe that \emph{platoon} pattern is to loose on the temporal domain thus may result in less significant patterns. For example in Figure~\ref{fig:platoon_weakpoint}.

%
%\begin{figure}[h]
%\center
%\includegraphics[width=0.5\textwidth]{platoon_weakpoint.eps}
%\caption{Miss-pattern in platoon}
%\label{fig:platoon_weakpoint}
%\end{figure}

%In platoon, a pattern for $n=2,k=4,l=2$ could be $\{o_1, o_2\}\{t_1,t_2,t_4,t_5,t_{100},t_{101}\}$. However, the snapshots $t_{100}$ and $t_{101}$ is too far away from previous snapshots. Such two snapshots are in less relation with previous snapshots and thus should be removed from the pattern. Based on this observation, we defined a \emph{generalized co-moving} pattern (as in Section~\ref{sec:definition}) to provide a more fine granular control of the pattern. In \emph{generalized co-moving} pattern, a parameter $g$ is introduce the control the \emph{maximum gap} allowed between consecutive snapshots. By so doing our generalized co-moving pattern is more expressive and can represent all the existing co-moving patterns.

%In step with the advances in localization technologies, the growth in the volume of trajectory data is rapid. Traditional single-machine methods face severe scalability problem in handling large trajectory data. For example, as reported in~\cite{li2015platoon}, a \emph{Swarm} pattern takes around 100 seconds to discover for 100k trajectories. With upto billions of trajectories in nowadays datasets, such approaches apparently become unfeasible. To tackle this challenge, we propose a  paralleled solution for discovering \emph{generalized co-moving} patterns. We then deploy our idea on the modern MapReduce platform. As our experiments show, our solution achieves well load-balance and can process billions of trajectories in XXX seconds. Several optimizations are also designed to boost our solution to be orders of magnitudes faster than baseline algorithms.

%In practice, it is cumbersome to design tailed solutions to different types of co-movement pattern discovery.

%In reality, it is cumbersome to design tailed solutions to support 
%generality and scalability

%In this paper, our primary objectives are solving two

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. 
The \emph{loose connection} problem refers to the patterns that discovered 
are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
\caption{Loosely connected pattern in platoon and swarm. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-movement patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & {\tiny Proximity} & {\tiny Consecutiveness} & {\tiny Time Complexity}\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|(M + log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & - & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering methods as a black-box and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\{o_3,o_4\}$ and $\{o_5,o_6\}$  remains the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\{o_1,o_2:1,2,4,5\}$ is a pattern matching local consecutiveness because timestamps $\{1,2\}$ and $\{4,5\}$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\{o_3,o_4,o_5:2,3\}$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

As can be seen, there are various co-movement patterns requested by different 
applications and it is cumbersome to design a tailored solution for each type. 
In addition, existing pattern definitions are not expressive enough and may miss 
interesting patterns or return noisy results. We summarize 
the two scenarios as \emph{missing-pattern} anomaly
and \emph{loose-connection} anomaly.
A \emph{missing-pattern} anomaly arises due to the stringent constraints on the pattern duration.
As shown in Figure~\ref{fig:platoon_weakpoint} (a), if we set $K=4$, 
neither \emph{flock}s nor \emph{convoy}s can be discovered. This is because
$o_1$ is away from $o_2$ at timestamp $4$, which is likely caused by
the traffic control or the clustering inaccuracy at time $4$. On the other hand,
the \emph{loose-connection} anomaly occurs due to an over-relaxed constraint on 
the duration. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
the two objects $o_1, o_2$ form a \emph{platoon} pattern 
$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
making the co-moving behavior very weak.
In reality, such an anomaly is likely to be induced by the periodic movements of unrelated objects 
such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
It is easy to see that none of the existing co-movement patterns are able to avoid these two anomalies.

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
in \emph{flock} and \emph{convoy}. When $K=4$, none of the two patterns can be discovered. (b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

%In current literature,
%users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
%
%
% we summarize two anomalies 
%The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
%Figure~\ref{fig:platoon_weakpoint} (a).  As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
%the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
%be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
%\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
%as \emph{loose-connection}~\cite{li2015platoon} anomaly. 
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.

%For instance, PUT THE FIGURE AND EXPLANATION HERE.

%\begin{figure}[h]
%\center
%\includegraphics[width=0.35\textwidth]{rw_perf_O.eps}
%\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
%in \emph{flock} and \emph{convoy}. When $K=4$, none of the two patterns can be discovered. (b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
%\label{fig:platoon_weakpoint}
%\end{figure}

The other issue with existing methods is that they are 
built on top of centralized indexes that are not scalable. 
To the best of our knowledge, the maximum number of trajectories 
ever evaluated is up to hundreds of trajectories. 
In practice, it is rather common to collect at least hundreds of thousands of trajectories 
and their scalability is left unknown. We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns}) as well as an experimental evaluation with a real trajectory database including million-scale points(as shown in Figure~\ref{fig:related_work_scalability}). 
Results show that their performances degrade dramatically as the dataset size scales up. For instances,
performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.5k} to \emph{2.4k}.
It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which may include billion-scale points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ objects}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1.2k$ timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with over 2 million points.}
    \label{fig:related_work_scalability}
\end{figure}

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way while avoids 
the two identified anomalies. In GCMP, we gain a
fine-grained control over pattern duration by introducing the gap 
parameter $G$, which enforces the gap between 
timestamps to be no larger than $G$.  
The adoption of $G$ seamlessly integrates with other pattern parameters,
which preserves the expressiveness while
alleviates both the \emph{missing-pattern} and the \emph{loose connection} anomalies.

%Therefore, users are 
%still able to exclude non-consecutive patterns 
%or include loosely-connected patterns when they feel necessary.

%We introduce the gap parameter $G$,
%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
%To cope with both of the two anomalies, we propose 
%by introducing the gap parameter $G$,

%By so doing, we gain a fine-grained control s, which As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?
%

Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
of the partitions. Such properties ensure that neither false-patterns 
nor miss-patterns are possible in our solution. To meet such partition requirements
as well as to keep the shuffle amount to a minimum, 
we first design a naive \emph{Temporal Replication and Mining} (TRM)
approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
Despite the simpleness of star partition, we theoretically prove its optimality.
Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
shuffling and mining cost in SPM. 
%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
%Apache Spark which is one of the most popular MapReduce platforms.

%we design a novel star-based partition scheme to efficiently partition objects based on their
%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

### 2016-05-28 sec5_baseline.tex
Added intro part

\begin{example}
We illustrate the process of TRM in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
for each partition, which equals to $(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Therefore, in (b), every four snapshots
are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
$C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1\}$ which is neither
a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
sweep finishes, only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

>>>>

\begin{example}
We illustrate the process of TRM in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
for each partition, which equals to $(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Therefore, in (b), every four snapshots
are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
$C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
patterns whose object set is in $S_1$. When scanning the snapshots, patterns in $C_1$ grow
their timestamps. At $S_4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2,4\}$ which is neither a qualified set of timestamps nor matches $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are scanned, 
only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

### 2016-05-28 sec6_spm.tex
Added intro part

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to develop a method that achieves good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we adapt an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsubsection{Star Partition}
The intuition of star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$}
\State { Ground $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Ground.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Ground;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in $Ground}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is partly valid} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

>>>>

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to achieve a good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we adapt an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsubsection{Star Partition}
The intuition of the star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State { Lv $\gets \{\}$,Ground $\gets \{\}$, Output $\gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State Ground.add($\langle \{s,t\}, T \rangle$);
\State Lv $\gets$ Ground;
\EndFor
\While{true}
	\If{Lv is not empty} 
		\State{LvCand $\gets \{\}$ }
		\ForAll{$cand_v \in Lv$}
			\ForAll{$cand \in $Ground}
				\State $p \gets cand_v$ join $cand$
				\If{$p.T$ is a candidate sequence} 
					\State LvCand.add($p$)
				\EndIf
			\EndFor
		\EndFor
		\If{$Lv$ is a pattern}
			\State{Output.add($Lv$)}
			\State{break}			 
		\EndIf
		\State {Lv $\gets$ LvCand}
	\Else
		\State{break}
	\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}
